\documentclass{grattan}
\usepackage{longtable, tabularx, hyperref}
\addbibresource{bib/HigherEd-Grattan.bib}
% add_to_dictionary: ATAR ATARs CHESSN EFTSL LSAY TEQSA UES llp IRSD voc-ed Voc-ed subbachelor var grattan Austudy EFTSLs reenrols TER VTAC RIASEC ealistic nvestigative rtistic ocial nterprising onventional preferencing SEIFA skilling HESA QILT api RMIT HEIMSHELP Hosmer-Lemeshow

\ReportOrWorkingPaper{Background Paper}         %% background paper is now on acknowledgement page
\GrattanReportNumber{2018-08}
\YEAR{2018}
\MONTH{March}

% editorial_author_only: James Ha

\author{Ittima Cherastidtham \& Andrew Norton}
\title{University attrition: what helps university completion?}

\acknowledgements{%
    This background paper was written by Andrew Norton, Grattan Institute Higher Education Program Director and Ittima Cherastidtham, Higher Education Program Fellow. Will Mackey provided extensive research assistance and made a substantial contribution to the report. James Ha also provided research assistance.

    We would like to thank Buly Cardak, Ian Li, members of Grattan Institute’s Higher Education Reference Group, and several others for their advice on this background paper.

    The opinions in this background paper are those of the authors and do not necessarily represent the views of Grattan Institute's founding members, affiliates, individual board members reference group members or reviewers.
    Any remaining errors or omissions are the responsibility of the authors.

    Grattan Institute is an independent think-tank focused on Australian public policy.
    Our work is independent, practical and rigorous.
    We aim to improve policy outcomes by engaging with both decision-makers and the community.

    For further information on the Institute's programs, or to join our mailing list, please go to: \textcolor{blue}{\url{http://www.grattan.edu.au/}}.

    {\footnotesize
    This background paper may be cited as:
    Cherastidtham, I., Norton, A., and Mackey, W\@. (2018). \emph{\mytitle}. Grattan Institute.

    ISBN: 978-0-6482307-8-6             %this is a separate ISBN for the background paper

    All material published or otherwise created by Grattan Institute is licensed under a Creative Commons Attribution-NonCommercial-ShareAlike 3.0 Unported License\par
    }
}


\begin{document}
\null
\end{document}

